\documentclass[9pt]{article}

\usepackage[parfill]{parskip}
\parskip 0pt

\usepackage{tabto}

%------No Page Nums---
\pagenumbering{gobble}
%------Dimensions-----
\usepackage[top=0.5in,left=0.25in,right=0.25in,bottom=0.5in]{geometry}


\begin{document}
  \centerline{
    \LARGE\textbf{Douglas J. Smith}
  }
  \centerline{
    School: 326 Stanford Hall, Notre Dame, IN 46556
    Email: dsmith47@nd.edu
    Github: dsmith47
  }
  \centerline{
    Home: 292 Krepp Rd, Cooperstown, PA 16317
  }

  \vspace{-16pt}
  \section*{Education}
    \vspace{-16pt}
    \line(1,0){580}\\
    University of Notre Dame
    \hfill
    2015-2019
    \\
    Bachelors of Science in Engineering
    \hfill
    GPA 3.44
    \\
    %Need the above to format that line, so the below is longer than normal. 
  \vspace{-28pt}
  \section*{Related Experience}
    \vspace{-16pt}
    \line(1,0){580}\\

    \textbf{Google, Inc.}
    \tab 
    Pittsburgh, PA
    \hfill 
    May 2017 - Present
    \\
    \textit{Engineering Practicum Intern}
    \begin{itemize}
      \item Built web application for comparing the results of A/B experiment tests on ad serving models.
      \item Implemented system for comparison of A/B experiments as a C++ binary.
      \item Designed user interface for summarizing and querying test data, then built using Angular2 following the Google Material design specification.
    \end{itemize}
  
    \textbf{Crcl}
    \tab
    Notre Dame, IN
    \hfill
    August 2016 - Present
    \\
    \textit{Android Developer / Project Manager, Web Developer}
    \begin{itemize}
      \item Coded Crcl-Android app based on business review functions/features of Crcl iOS application.
      \item Contributed to completion of Crcl's Angular2 web application.
      \item Integrated Google Analytics on Web and Angular applications.
      \item Improving Android features and maintaining application post-launch.
    \end{itemize}
    
    \textbf{Notre Dame Department of Computer Science}
    \tab
    Notre Dame, IN
    \hfill
    September 2016 - Present
    \\
    \textit{Student Researcher for Dr. Ronald Metoyer}
    \begin{itemize}
      \item Building Swift iOS applications focused on utilizing two device cameras simultaneously.
      \item Wrote python script for creating D3-readable JSON from survey data.
      \item Constructed HCI lab website using AngularJS and BootstrapCSS.
    \end{itemize}
    
    \textbf{Arrix Family Mobile Development Lab}
    \tab
    Notre Dame, IN
    \hfill
    January 2017 - Present
    \\
    \textit{Software Developer}
    \begin{itemize}
      \item Originating, designing, and developing applications for student use at the university in conjunction with OIT and the Athletics Department. Building application with Django backend and ReactJS frontend.
    \end{itemize}
    
    \textbf{Notre Dame Department of Theatre}
    \tab
    Notre Dame, IN  
    \hfill
    August 2016 - May 2017
    \\
    \textit{Database Admin/Teaching Assistant}
    \begin{itemize}
      \item Created site for managing student work scheduling using a PHP script interacting with a PostgreSQL database.
      \item Oversaw hosting/database management for scheduling website using first Heroku and then a private server.
    \end{itemize}
    
    \textbf{National Tsing Hua University}
    \tab
    Hsinchu, Taiwan
    \hfill
    May 2016 - August 2016
    \\
    \textit{Researcher}
    \begin{itemize}
      \item Designed system for dynamically testing circuits and fault lists for identical faults with a C++ binary that decomposed fault descriptions to test for equivalent outputs.
      \item Refactored ABC circuit modeling library to function with C/C++ executables, optimizing for modeling purposes.
    \end{itemize}
    
    \textbf{Mercatus}
    \tab
    San Mateo, CA
    \hfill
    February 2016 - March 2016
    \\
    \textit{Software Intern}
    \begin{itemize}
      \item Developed python script for producing Excel spreadsheets with summaries from GoodData, Jira, and ZenDesk APIs.
      \item Wrote script converting GoodData reports to PowerPoint presentations.
    \end{itemize}
    
    \textbf{Promazo}
    \tab
    Notre Dame, IN
    \hfill
    March 2016 - August 2016
    \\
    \textit{Web Development Consultant}
    \begin{itemize}
      \item Instituted small maintenance changes to Promazo website 1.0.
      \item Contributed to website design/feature layout for website 2.0.
      \item Engineered tests for website 2.0 REST API, implented in Django framework.
    \end{itemize}
  
    \textbf{11trees}
    \tab
    Austin, TX
    \hfill
    April 2015 - January 2017
    \\
    \textit{Software Development Consultant}
    \begin{itemize}
      \item Designed, coded, and tested Annotate for Chrome extension, which expanded user's copy-paste ability in Chrome.
      \item Updated/maintained Annotate for Chrome post-release for increased security/performance.
      \item Developed Alpha version of Annotate for Word, porting Annotate style/features to Microsoft's Javascript Add-On framework.
    \end{itemize}
 

  \vspace{-16pt}
  \section*{Projects}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textbf{Chromex} - Command line utility for interacting with google applications from the omnibox of any extensible chromium-based browser.
    \\
    \textbf{ServeLite} - Exercise in creating a high-performing server that issmall in size and recomilable for different features.
    \\
    \textbf{Jeeves} - Multiplatform application that presents a series of customizable sub-applications built in Ionic framework.

  \vspace{-16pt}
  \section*{Leadership/Activities}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textit{Band of the Fighting Irish}
    -
    Marching Alto Saxophone, Varsity Hockey/Basketball Band
    \\
    \textit{Student Government}
    -
    Department of Campus technology CTO
    \\
    \textit{Linux User Group}
    -
    Web development team
    
  \vspace{-16pt}
  \section*{Skills}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textbf{Skills}
    Software Engineering,
    Full Stack Development,
    UI/UX Design,
    Linux
    \\
    \textbf{Programming Languages}
    C,
    C++,
    Java,
    Bash,
    Python,
    Ruby,
    Perl,
    Closure,
    Typescript/Javascript,
    HTML,
    CSS/LESS/SASS
    \\
    \textbf{Databases}
    SQL,
    MongoDB,
    Firebase
    \\
    \textbf{Frameworks}
    Django,
    Angular,
    ReactJS
    \\
    \textbf{Tools}
    Git,
    Perforce,
    Bazel,
    \\
\end{document}


