\documentclass[9pt]{article}

\usepackage[parfill]{parskip}

%------No Page Nums---
\pagenumbering{gobble}
%------Dimensions-----
\usepackage[top=0.5in,left=0.25in,right=0.25in,bottom=0.5in]{geometry}

\parskip 0pt

\begin{document}
  \centerline{
    \LARGE\textbf{Douglas J. Smith}
  }
  \centerline{
    School: 326 Stanford Hall, Notre Dame, IN 46556
    Email: dsmith47@nd.edu
    Github: dsmith47
  }
  \centerline{
    Home: 292 Krepp Rd, Cooperstown, PA 16317
  }

  \vspace{-16pt}
  \subsection*{Education}
    \vspace{-16pt}
    \line(1,0){580}\\
    University of Notre Dame
    \hfill
    2015-2019
    \\
    Bachelors of Science in Engineering
    \hfill
    GPA 3.44
    \\
    %Need the above to format that line, so the below is longer than normal. 
  \vspace{-28pt}
  \subsection*{Related Experience}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textbf{Google, Inc.}
    \hfill
    Pittsburgh, PA
    \hfill
    May 2017 - Present
    \\
    \textit{Engineering Practicum Intern}
    \begin{itemize}
      \item Built full stack web application for comparing the results of factual and counterfactual experiments testing Ad serving models.
      \item Implemented system for comparison of factual/counterfactual experiments as a C++ binary that performs a series of tests to differentiate experimental results.
      \item Developed web frontend to summarize and query test data with Angular 2 following the Google Material Design Specification.
    \end{itemize}
  
    \textbf{Crcl}
    \hfill
    Notre Dame, IN
    \hfill
    August 2016 - Present
    \\
    \textit{Android Developer / Project Manager, Web Developer}
    \begin{itemize}
      \item Coded Crcl-Android app based on business review functions/features of Crcl iOS application.
      \item Contributed to completion of Crcl's Angular2 web application.
      \item Integrated Google Analytics on Web and Angular applications.
      \item Improving Android features and maintaining application post-launch.
    \end{itemize}
    
    \textbf{Notre Dame Department of Computer Science}
    \hfill
    Notre Dame, IN
    \hfill
    September 2016 - Present
    \\
    \textit{Student Researcher for Dr. Ronald Metoyer}
    \begin{itemize}
      \item Wrote python script for creating D3-readable JSON from survey data.
      \item Constructed HCI lab website using AngularJS and BootstrapCSS.
      \item Building Swift iOS applications focused on utilizing two device cameras simultaneously.
    \end{itemize}
    
    \textbf{Arrix Family Mobile Development Lab}
    \hfill
    Notre Dame, IN
    \hfill
    January 2017 - Present
    \\
    \textit{Software Developer}
    \begin{itemize}
      \item Originating, designing, and developing applications for student use at the university in conjunction with OIT and the Athletics Department. Building application with Django backend and ReactJS frontend.
    \end{itemize}
    
    \textbf{Notre Dame Department of Theatre}
    \hfill
    Notre Dame, IN  
    \hfill
    August 2016 - May 2017
    \\
    \textit{Database Admin/Teaching Assistant}
    \begin{itemize}
      \item Created site for managing student work scheduling using a PHP script interacting with a PostgreSQL database.
      \item Oversaw hosting/database management for scheduling website using first Heroku and then a private server.
    \end{itemize}
    
    \textbf{National Tsing Hua University}
    \hfill
    Hsinchu, Taiwan
    \hfill
    May 2016 - August 2016
    \\
    \textit{Researcher}
    \begin{itemize}
      \item Designed system for dynamically testing circuits and fault lists for identical faults with a C++ binary that decomposed fault descriptions to test for equivalent outputs.
      \item Refactored ABC circuit modeling library to function with C/C++ executables, optimizing for modeling purposes.
    \end{itemize}
    
    \textbf{Mercatus}
    \hfill
    San Mateo, CA
    \hfill
    February 2016 - March 2016
    \\
    \textit{Software Intern}
    \begin{itemize}
      \item Developed python script for producing Excel spreadsheets with summaries from GoodData, Jira, and ZenDesk APIs using openpyxl library.
    \end{itemize}
    
    \textbf{11trees}
    \hfill
    Austin, TX
    \hfill
    April 2015 - January 2017
    \\
    \textit{Software Development Consultant}
    \begin{itemize}
      \item Designed, coded, and tested Annotate for Chrome extension, which expanded user's copy-paste ability in Chrome.
      \item Developed Alpha version of Annotate for Word, porting Annotate style/features to Microsoft's Javascript Add-On framework.
    \end{itemize}
 

  \vspace{-16pt}
  \subsection*{Projects}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textbf{Chromex} - Command line utility for interacting with google applications from the omnibox of any extensible chromium-based browser.
    \\
    \textbf{ServeLite} - Exercise in creating a high-performing server that issmall in size and recomilable for different features.
    \\
    \textbf{Jeeves} - Multiplatform application that presents a series of customizable sub-applications built in Ionic framework.

  \vspace{-16pt}
  \subsection*{Leadership/Activities}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textit{Band of the Fighting Irish}
    -
    Marching Alto Saxophone, Varsity Hockey/Basketball Band
    \\
    \textit{Student Government}
    -
    Department of Campus technology CTO
    \\
    \textit{Linux User Group}
    -
    Web development team
    
  \vspace{-16pt}
  \subsection*{Skills}
    \vspace{-16pt}
    \line(1,0){580}\\
    \textbf{Skills}
    Software Engineering,
    Full Stack Development,
    UI/UX Design,
    Linux
    \\
    \textbf{Programming Languages}
    C,
    C++,
    Java,
    Bash,
    Python,
    Ruby,
    Perl,
    Closure,
    Typescript/Javascript,
    HTML,
    CSS/LESS/SASS
    SQL,
    MongoDB,
    Firebase
    \\
\end{document}


